\documentclass[11pt]{article}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{tcolorbox}
\usepackage{enumerate}

\newcommand{\zo}{\{0,1\}}


\begin{document}

    \pagestyle{fancy}
    \fancyhead[C]{\textbf{Basic Algorithms (Section 1)}\\Fall 2022}
    \fancyhead[R]{HW0\\ Instructor: Marshall Ball}
    \fancyfoot[C]{}
    \fancyfoot[R]{\thepage}
    \renewcommand{\headrulewidth}{0.4pt}
    \renewcommand{\footrulewidth}{2pt}
    
    %%%% EDIT THIS PART 
    %Put your name and Net ID here
	\fancyhead[L]{Name:  \\ Net ID: }
    %Write your collaborators' names here
    \fancyfoot[L]{Discussion Partners:}
    %%%%%
	

    %Problem 1A
    \begin{tcolorbox}[title={Problem 1A (Summations, A.1-4)}]
    Prove the following equality for all real $a \neq 1$ and for all $n \geq 1$ by induction on $n$:
    $$
    1 + a + a^2 + \ldots + a^n = \frac{1-a^{n+1}}{1-a}.
    $$
    \begin{enumerate}
        \item Prove the base of induction $n=1$.
        \item Prove the inductive step.
        \item Use the result to evaluate the series $1 - \frac{1}{2} + \frac{1}{4} - \frac{1}{8}+\frac{1}{16}-\cdots$.
    \end{enumerate}
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    %Problem 1B
    \begin{tcolorbox}[title={Problem 1B (Bounds, A.2-1)}]
        Show that $\sum_{k=1}^n \frac{1}{k^2}$ is bounded from above by a constant.
        
        {\it Hint: you can prove this inductively by bounding the $n$th sum with $2-\frac{1}{n}$}
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
    %Problem 2A
    \begin{tcolorbox}[title={Problem 2A (Sets, B.1-4)}]
        Show that the set of powers of 2, $\{\ldots,\frac{1}{4},\frac{1}{2},1,2,4,8,16\ldots\}$ is countable.
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    %Problem 2B
    \begin{tcolorbox}[title={Problem 2B (Functions, B.3-1)}]
       Let $A$ and $B$ be finite sets and let $f:A\to B$ be a function. Show the following:
       \begin{enumerate}[(a)]
           \item If $f$ is injective, then $|A|\le |B|$.
           \item If $f$ is surjective, then $|B| \le |A|$.
       \end{enumerate}
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
    
    %Problem 2C 
    \begin{tcolorbox}[title={Problem 2C (Graphs, B.4-3)}]
       Show by induction on $|E|$ that for and undirected graph $G=(V,E)$ the number of connected components is at least $|V| - |E|$.
       \begin{enumerate}
           \item Prove the base of induction: $|E|=0$.
           \item Prove the inductive step.
           \item Deduce from the obtained result that any connected, undirected graph $G=(V,E)$ satisfies $|E|\ge |V|-1$.
           \item A connected undirected graph has 6 vertices and 6 edges. Can we say that it is connected? Either prove that this is true for all such graphs, or provide a counterexample.
       \end{enumerate}
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
    %Problem 2D
    \begin{tcolorbox}[title={Problem 2D (Trees, B.5-5)}]
       Use induction to show that any non-empty binary tree with $n$ vertices has height at least $\lfloor \log_2(n) \rfloor$
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
    %Problem 3A
    \begin{tcolorbox}[title={Problem 3A (Counting, C.1-2)}]
       An $n$-input $m$-output boolean function is a function from $\zo^n$ to $\zo^m$. 
       \begin{enumerate}
            \item What is the size of the set $\zo^n$?
           \item How many $n$-input $1$-output boolean functions are there?
           \item How many $n$-input $m$-output boolean functions are there?
       \end{enumerate}

    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
        %Problem 3B
    \begin{tcolorbox}[title={Problem 3B (Counting, C.1-9)}]
       Prove the following:
       \[ \sum_{i=1}^n i = \binom{n+1}{2}\]
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
    %Problem 3C
    \begin{tcolorbox}[title={Problem 3C (Probability, C.2-4)}]
        Prove that for any events $A$ and $B$:
        \[ \Pr[A|B] + \Pr[\neg A |B] =1\]
    \end{tcolorbox}
    %Write your solution here!
    
    \newpage
    
    %Problem 3D
    \begin{tcolorbox}[title={Problem 3D (Discrete Random Variables, C.3-1)}]
        You roll two (unbiased) 20-sided dice. What is the expectation of the sum of the two values showing? What is the expectation of the maximum of the two values showing?
    \end{tcolorbox}
    %Write your solution here!

    
    
\end{document}